---
title: "Model Evaluation"
author: "Vivek Kantamani (vk2389)"
geometry: margin = 1.25cm
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 10.5pt
---

Our function which wraps our final model, takes gene expression levels as input, and returns the prediction of patients' status is provided below.  
Please ensure that the (1) test data set, and (2) file `final_model.RDS` exist in the same directory as this RMD file.  
Please insert the name of the test data set to be assigned to the object `test_data`.  

```{r}
# PLEASE INSERT TEST DATA SET NAME HERE
# REPLACE "breast_cancer_test.csv" WITH THE NAME OF THE TEST DATA SET
test_file = "breast_cancer_test.csv"

library(e1071)

# Function argument is the test data set
model_function = function(test_file) {
  
  # Read in test data set
  test_data = read.csv(test_file)
  
  # Load final model using readRDS()
  final_model = readRDS(file = "final_model.RDS")
  
  # Predict the class labels for the test data set
  pred = predict(final_model, test_data)
  
  # Return the prediction of patients' status
  return(pred)
}

prediction = model_function(test_file)

paste("The predictions of patients' status is as follows.")
prediction
```

If the test data set is normalized, filtered, and labeled similarly to the training data set, then the following code will produce a confusion matrix and determine the test error of the model applied to the test data set.  

```{r}
# Read in test data set
test = read.csv(test_file)

# Produce a confusion matrix 
confusion_matrix = table(prediction, test$status)
paste("A confusion matrix of the results of the model on the test data set is as follows.")
confusion_matrix

# Calculate the test error of the model
error = mean(prediction != test$status)
paste("The test error is ", error,
      sep = "")
```